\color{dark-maroon} Differences-in-Differences with Spatial Spillover

### 2020-11-28 latex/paper/paper.tex
Edits to paper draft

% ------------------------------------------------------------------------------
\subsection{Improving Estimation}
% ------------------------------------------------------------------------------

@@

There are a few practical considerations researchers should make when parametrizing the spillovers.

@@

% ------------------------------------------------------------------------------
\subsection{Simulation 1: Spillover on Controls Only}
% ------------------------------------------------------------------------------

@@

A common solution in the literature is to remove control units from the estimated sample that are most likely to be affected by spillovers. I do this in Figure \ref{fig:bias_as_treat_prob} and the results are shown by the line with circle markers. Even though, I remove contiguous controls which is not hte correct measure of $h_i(\vec{D})$, it approximates it well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed. As the portion of control units receiving spillovers that are kept in the sapmle increases, the bias would fall between the two lines.

@@

% -----------------------------------------------------------------------------
\subsection{Simulation 2}
% ------------------------------------------------------------------------------

@@

@@

@@

I will focus on three outcome variables in the analysis. The first two are (the log of) agricultural and manufacturing employment and the last is (the log of) median household income. Since the TVA focused on manufacturing employment, the authors predict that employment will grow in manufacturing and shrink in agricultural. Since manufacturing jobs pay more on average, the median household income will therefore grow.

There are two primary forces causing spillover in this context. First, the large-scale investment in dams and electricity transmission lines brought cheap power to the region. It became cheaper for nearby locations to get connected to low-cost power and therefore likely lead to transition to manufacturing and away from farming in nearby counties. Second, \citet{Duranton_Puga_2003} highlight the agglomeration of input sourcing. When the Authority has a large increase in manufacturing, they develop resource supply chains that in turn make inputs cheaper for neighboring counties. These both suggest that spillovers will occur close to the spillover region and that the exposure will decay over distance.

The analysis in \citet{Kline_Moretti_2014} begins by comparing long-differences in county-level outcomes from 1940 to 2000 between treated counties in the Authority and control counties outside. The primary difference-in-differences specification is
\begin{equation}\label{eq:tva}
    y_{c, t} = \mu_c + \alpha \text{Post}_t + \tau \text{TVA}_c \times \text{Post}_t + X_{c, 1940} \beta + X_{c, 1940} \times \text{Post}_t \gamma + \epsilon_{c,t},
\end{equation}
where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ equals one when $t = 2010$ and equals zero when $t = 1940$, and $y$ is a series of outcome variables.\footnote{The text writes the equivalent first-differences regression: \[ 
    y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} (\gamma - \beta) + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940}). 
\] Outcome variables are all in logs and include population, average manufacturing wage, agricultural employment, manufacturing employment, value of farm production, median family income, and median housing value.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.}

@@

The authors use an Oaxaca-Blinder estimator on the first differences and the results of \citet{Kline_2011} show that this estimator is a weighted difference-in-differences. The weights can be seen in Figure III of their text, but generally counties close to the TVA are upweighted. Hence, their method magnifies the bias compared to a standard difference-in-differences estimator.  However, in Table \ref{tab:tva} below, I will show their estimator does not differ much from the standard difference-in-differences results.

I extend their analysis to include spatial spillovers in the difference-in-differences specification. To parametrize the exposure mapping, I include a set of indicator variables for being in distance bins away from the Authority. Specifically, I use the following intervals $\text{Dist} = \{(0, 100], (100, 250], (250, 500]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority. The extended specification is given as follows:  
\begin{equation}\label{eq:tva_spillover}
    y_{i, 2000} - y_{i, 1940} = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + (\varepsilon_{i, 2000} - \varepsilon_{i, 1940})
\end{equation} 
The coefficients $\delta_d$ measure the spillover effect at different distances from the Authority.

>>>>

% ------------------------------------------------------------------------------
\subsection{Improving Estimation by Parameterizing Spillovers}
% ------------------------------------------------------------------------------

@@

There are a few practical considerations researchers should make when parametrizing the spillovers. % @TODO: Expand upon considerations in the introduction

@@

% ------------------------------------------------------------------------------
\subsection{Spillover on Controls Only}
% ------------------------------------------------------------------------------

@@

A common solution in the literature is to remove control units from the estimated sample that are most likely to be affected by spillovers. I do this in Figure \ref{fig:bias_as_treat_prob} and the results are shown by the line with circle markers. Even though, I remove contiguous controls which is not the correct measure of $h_i(\vec{D})$, it approximates it well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed. As the portion of control units receiving spillovers that are kept in the sapmle increases, the bias would fall between the two lines.

@@

% -----------------------------------------------------------------------------
\subsection{Spillovers onto Control and Treated Units}
% ------------------------------------------------------------------------------

@@

In order to model spatial autocorrelation of treatment, I turn to a method from geosciences called `kriging'. Kriging generates a Gaussian field for a large grid of points across the entire United States where the spatial autocorrelation of the points is described by a set of parameters. One such field is depicted in Figure \ref{fig:kriging}. For a given field, I find the counties in the top ten percent of values and give these counties a value of $\text{Zone}_i = 1$. Then I assign treatment with a probability that differs based on Zone. The unconditional probability is equal to 5 percent in all simulations. To do this, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment: 
\begin{equation}
    \label{eq:cond_prob}
    P(D_i \ \vert \ \text{Zone}_i) = (.1 + \text{Zone Plus} * \text{Zone}_i) \times \frac{.05}{.1 * .9 + (.1 + \text{Zone Plus}) * .1}
\end{equation}
The second term normalizes probabilities so the unconditional probability stays at five percent. In our simulations, Zone Plus ranges from 0 which is the case where p = five percent for all counties to 2 which has $P(D_i \ \vert \ \text{Zone}_i) = 0.0166 + 0.35 * \text{Zone}_i$

@@

% ------------------------------------------------------------------------------
\subsection{Misspecification of Spillovers}
% ------------------------------------------------------------------------------

% @ TODO

@@

\citet{Kline_Moretti_2014} focus on a set of outcome variables, but I will focus on three in the analysis. The first two are (the log of) agricultural and manufacturing employment and the last is (the log of) median household income. Since the TVA focused on manufacturing employment, the authors predict that employment will grow in manufacturing and shrink in agricultural. Since manufacturing jobs pay more on average, the median household income will therefore grow.

There are two primary forces causing spillover in this context. First, the large-scale investment in dams and electricity transmission lines brought cheap power to the region. It became cheaper for nearby locations to get connected to low-cost power and therefore this likely caused a transition to manufacturing and away from farming in nearby counties. Second, \citet{Duranton_Puga_2003} highlight the agglomeration of input sourcing. When the Authority has a large increase in manufacturing, they develop resource supply chains that in turn make inputs cheaper for neighboring counties. These both suggest that spillovers will occur close to the spillover region and that the exposure will decay over distance.

The analysis in \citet{Kline_Moretti_2014} begins by comparing long-differences in county-level outcomes from 1940 to 2000 between treated counties in the Authority and control counties outside. The primary difference-in-differences specification is
\begin{equation}\label{eq:tva}
    y_{c, t} = \mu_c + \alpha \text{Post}_t + \tau \text{TVA}_c \times \text{Post}_t + X_{c, 1940} \beta + X_{c, 1940} \times \text{Post}_t \gamma + \epsilon_{c,t},
\end{equation}
where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ equals one when $t = 2010$ and equals zero when $t = 1940$, and $y$ is a set of outcome variables.\footnote{The text writes the equivalent first-differences regression: \[ 
    y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} (\gamma - \beta) + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940}). 
\] Outcome variables are all in logs and include population, average manufacturing wage, agricultural employment, manufacturing employment, value of farm production, median family income, and median housing value.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.}

@@

The authors use an Oaxaca-Blinder estimator on the first differences and the results of \citet{Kline_2011} show that this estimator is a weighted difference-in-differences. The weights can be seen in Figure III of their text, but generally counties close to the TVA are upweighted. Hence, their method magnifies the bias compared to a standard difference-in-differences estimator.  However, in Table \ref{tab:tva} below, I will show their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform.

I extend their analysis to include spatial spillovers in the difference-in-differences specification. To parametrize the exposure mapping, I include a set of indicator variables for being in distance bins away from the Authority. I do this for two reasons. Specifically, I use the following intervals $\text{Dist} = \{(0, 100], (100, 250], (250, 500]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority. As discussed above, I suspect the spillover to decrease as counties move further away, hence I allow the effect to be seperately identified in bins. However, I

The specification with spillovers is given as follows:  
\begin{equation}\label{eq:tva_spillover}
    y_{i, 2000} - y_{i, 1940} = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + (\varepsilon_{i, 2000} - \varepsilon_{i, 1940})
\end{equation} 
The coefficients $\delta_d$ measure the spillover effect at different distances from the Authority.
